THESIS PROJECT PROPOSAL

### 2019-11-08 project_ashish/paper.tex
commit

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 6}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 6}
\end{figure}
